<a name="create_new_template"></a>

# Create new form template
The user can also create a complete new template. It is recommended,  however, that the user take advantage of the already existing forms to create their own templates. Therefore, the recommendation is to copy an old form and modify it.

The forms currently available are organized by meteorological service and time period. The form templates currently available are:

```{r, echo = FALSE}
formsPath <- file.path("keyEntry_standalone", "keyEntry_App", "www","forms")
formsPath1 <- normalizePath(file.path("..", "..", "forms"))
metServices <- list.files(formsPath1)
timePeriods <- unique(sapply(1:length(metServices), function(i){
  timePeriods <- list.files(file.path(formsPath1, metServices[i]))
})
)


df <- data.frame(matrix(NA, nrow = length(timePeriods), ncol = length(metServices)))

colnames(df) <- metServices
rownames(df) <- timePeriods

fileNames <- list.files(formsPath1, recursive = T)
matrix.new <- sapply(1:length(metServices), function(i){
  fileNames1 <- grep(metServices[i], fileNames)
  sapply(1:length(timePeriods), function(i2){
    fileNames2 <- grep(timePeriods[i2], fileNames[fileNames1])
    if (length(fileNames2)==0){
      values <- ""
    }else{
      values <- paste0(basename(fileNames[fileNames1]), collapse = ", ")
    }
  })
})

df.new <- as.data.frame(matrix.new)
colnames(df.new) <- metServices
rownames(df.new) <- timePeriods
library(knitr)
kable(df.new,align = "c")

```

and are located in the folder:

```{r, echo = FALSE}
cat(formsPath)
```

Once the new template has been created, it will be automatically available in the `keyEntry_App`.
