# Requirements

## Software requirements
The following software is required for the installation of the App:

* Windows 7 or higher
* Java SE Runtime Environment 7 or higher (<http://www.oracle.com/technetwork/java/javase/downloads/index.html>)
*	R v3.2.1 or higher (<https://cran.r-project.org/bin/windows/base/>)
*	RStudio v0.99.467 or higher (<https://www.rstudio.com/products/rstudio/download/>)
*	Rtools v.3.2 or higher (<https://cran.r-project.org/bin/windows/Rtools/>)
* A web-browser, such as Mozilla-Firefox, Chrome or Internet Explorer (v.11 or higher)

Besides this software, the App also requires additional programs to be fully operational:

* Pandoc (<http://pandoc.org/>): A universal document converter. It will be required to build up the help files.

If this program is not available in the localhost, the App will install it automatically. The following Table shows the default version that the App will install, as well as the links to the download file. The user can install a later version of the software at any time.

| Program       | Default version | Link to downloader                         |
| ------------- |:----------------| -------------------------------------------|
| Pandoc        | v1.19.2.1       | <http://pandoc.org/installing.html>        |

## R-Packages
The package is the fundamental unit of shareable code in R. A package bundles together code, data, documentation, etc. and is easy to share with others ([Wickham, 2017](#references)).

The keyEntry-App requires a number of R-packages to run properly. Most of them are available on-line and will be installed automatically by the App. These packages are:

<div class = "row">
<div class = "col-md-4">
```{r,  warning = FALSE, echo = FALSE}
cat(paste0(pkgs[[1]][1:3], collapse = "\n"))
```
</div>
<div class = "col-md-4">
```{r, warning = FALSE, echo=FALSE}
cat(paste0(pkgs[[1]][4:6], collapse = "\n"))
```
</div>
<div class = "col-md-4">
```{r,  warning = FALSE, echo = FALSE}
cat(paste0(pkgs[[1]][7:length(pkgs[[1]])], collapse = "\n"))
```
</div>
</div>

The packages are saved in the following path:
```{r, echo=FALSE}
cat(RpkgsDir)
```

